---
title: 'Analyses for CCL: Climate Advocacy Experiences'
author: "Michelle Shteyn Handy"
date: "3/29/2021"
output: 
  html_document:
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Attach packages
library(tidyverse)
library(here)
```

# Read in data and do some wrangling:
Remove participants who:

- Had less than 90% progress
- Completed study in less than 3 minutes
- Had more than 50% NAs on responses

```{r}

```

Reverse code ranking items such that higher scores indicate greater importance of the reasons for supporting the Energy Innovation & Carbon Dividend Act:

```{r}

```


# Descriptives

```{r}

```


# T-tests

Group participants into liberal or conservative bins. Then, conduct t-tests to see if liberals and conservatives significantly differ on which items they 

```{r}
# Use mutate, case_when to assign Ss into either liberal or conservative


# Conduct 8 t-tests: one on each reason
```


# Text and sentiment analysis

## Why did you get involved with climate advocacy? What were the factors that led you to get involved with CCL?


## What feedback do you have about your experience volunteering with CCL? Is it a welcoming space for you as a volunteer?









